Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-07-03 paper/paper.tex
simplify code

Then to effectively construct the meta-continuation @new_mcont@, we define an auxiliary function
@makeMCont@, which takes a list of closures as arguments and returns the meta-continuation. 
Function @makeMCont@ is a recursive function where the recursive invocation happens when 
constructing the meta-continuation based on the rest of closures set. 
Now we can dynamically generate the meta-continuation inside of a meta-continuation.
Meanwhile, the @new_cont@ we defined above is used here, simply because different closures 
actually share the same continuation.
The case where the empty closures set occurs is also interesting. At this case,
the continuation simply applies its meta-continuation @m@, and the meta-continuation of @aeval@
is the outer meta-continuation @mcontinue@. It would be clear if we inductively think the base case 
where the set contains only one closure, then @makeMCont@ is invoked with an empty set, 
therefore the continuation should do nothing. %TODO: rewrite this part.

\begin{lstlisting}
  def makeMCont(cls: List[Clos]): MCont = {
    val mcont: MCont = { case (config, seen) =>
      if (cls.isEmpty) aeval(config, seen, (c, seen, m) => m(c, seen), mcontinue)
      else {
        val Clos(Lam(v, body), c_env) = cls.head
        val baddr = allocBind(v, new_time);  val new_env = c_env + (v -> baddr)
        val new_store = store.update(baddr, argvs)
        aeval(Config(body, new_env, new_store, new_time), seen, new_cont, makeMCont(cls.tail))
      }
    } mcont }
  val new_mcont: MCont = makeMCont(closures.tail)
\end{lstlisting}

@@

\begin{lstlisting}
  def analyze(e: Expr): Set[Config] =
    aeval(inject(e), Set(), { (c, seen, m) => m(c, seen) }, { (c, seen) => seen })
\end{lstlisting}

@@

\begin{lstlisting}
  case class Ans(vss: Set[VS], cache: Cache) {
    def ++(ans: Ans): Ans = { Ans(vss ++ ans.vss, cache.join(ans.cache)) } }
\end{lstlisting}

@@

\begin{lstlisting}
  def nd[T](ts: Iterable[T], acc: Ans, f: (T, Cache, Ans => Ans) => Ans, m: Ans => Ans): Ans = {
    if (ts.isEmpty) m(acc)
    else f(ts.head, acc.cache, (ans: Ans) => nd(ts.tail, acc ++ ans, f, m))
  }
\end{lstlisting}

>>>>

Then to effectively construct the meta-continuation @new_mcont@, we define an auxiliary function
@makeMCont@, which takes a list of closures as arguments and returns the meta-continuation. 
Function @makeMCont@ is a recursive function where the recursive invocation happens when 
constructing the meta-continuation based on the rest of closures set. 
Now we can dynamically generate the meta-continuation inside of a meta-continuation.
Meanwhile, the @new_cont@ we defined above is used here, simply because different closures 
actually share the same continuation.
The case where the empty closures set occurs is also interesting. At this case,
the outer meta-continuation @mcontinue@ is returned.
It would be clear if we inductively think the base case where the closures set contains only one 
closure, then @makeMCont@ is invoked with an empty set, therefore should be just the 
current meta-continuation @mcontinue@.

\begin{lstlisting}
  def makeMCont(cls: List[Clos]): MCont =
    if (cls.isEmpty) mcontinue else { (config, seen) =>
      val Clos(Lam(v, body), c_env) = cls.head
      val baddr = allocBind(v, new_time);  val new_env = c_env + (v -> baddr)
      val new_store = store.update(baddr, argvs)
      aeval(Config(body, new_env, new_store, new_time), seen, new_cont, makeMCont(cls.tail)) }
  val new_mcont: MCont = makeMCont(closures.tail)
\end{lstlisting}

@@

\begin{lstlisting}
  def analyze(e: Expr): Set[Config] =
    aeval(inject(e), Set(), (c, seen, m) => m(c, seen), (c, seen) => seen)
\end{lstlisting}

@@

\begin{lstlisting}
  case class Ans(vss: Set[VS], cache: Cache) {
    def ++(ans: Ans): Ans = Ans(vss ++ ans.vss, cache.join(ans.cache)) }
\end{lstlisting}

@@

\begin{lstlisting}
  def nd[T](ts: Iterable[T], acc: Ans, f: (T, Cache, Ans => Ans) => Ans, m: Ans => Ans): Ans =
    if (ts.isEmpty) m(acc)
    else f(ts.head, acc.cache, (ans: Ans) => nd(ts.tail, acc ++ ans, f, m))
\end{lstlisting}
